Automated assessment of residual plots with computer vision models

### 2024-04-29 paper/cnn.tex
revise up to model arch

\def\ConvColor{rgb:yellow,5;red,2.5;white,5}
\def\ConvReluColor{rgb:yellow,5;red,5;white,5}
\def\PoolColor{rgb:red,1;black,0.3}
\def\FcColor{rgb:blue,5;red,2.5;white,5}
\def\FcReluColor{rgb:blue,5;red,5;white,4}
\def\SoftmaxColor{rgb:magenta,5;black,7}
\def\SumColor{rgb:blue,5;green,15}

@@

% conv1_1,conv1_2
\pic[shift={(0,0,0)}] at (0,0,0) {RightBandedBox={name=cr1,caption=Convolutional block 1,%
        xlabel={{"32","32"}},ylabel=32,zlabel=32,fill=\ConvColor,bandfill=\ConvReluColor,%
        height=40,width={2,2},depth=40}};
%pool1
\pic[shift={(0,0,0)}] at (cr1-east) {Box={name=p1,%
        fill=\PoolColor,opacity=0.5,height=35,width=1,depth=35}};
%%%%%%%%%%
% conv2_1,conv2_2
\pic[shift={(2,0,0)}] at (p1-east) {RightBandedBox={name=cr2,caption=Convolutional block 2,%
        xlabel={{"64","64"}},zlabel=16,fill=\ConvColor,bandfill=\ConvReluColor,%
        height=35,width={3,3},depth=35}};
%pool2
\pic[shift={(0,0,0)}] at (cr2-east) {Box={name=p2,%
        fill=\PoolColor,opacity=0.5,height=30,width=1,depth=30}};
%%%%%%%%%%
% conv3_1,conv3_2
\pic[shift={(2,0,0)}] at (p2-east) {RightBandedBox={name=cr3,caption=Convolutional block 3,%
        xlabel={{"128","128","128"}},zlabel=8,fill=\ConvColor,bandfill=\ConvReluColor,%
        height=30,width={4,4,4},depth=30}};
%pool3
\pic[shift={(0,0,0)}] at (cr3-east) {Box={name=p3,%
        fill=\PoolColor,opacity=0.5,height=23,width=1,depth=23}};
%%%%%%%%%%
% conv4_1,conv4_2,conv4_3
\pic[shift={(1.8,0,0)}] at (p3-east) {RightBandedBox={name=cr4,caption=Convolutional block 4,%
        xlabel={{"256","256","256"}},zlabel=4,fill=\ConvColor,bandfill=\ConvReluColor,%
        height=23,width={7,7,7},depth=23}};
%pool4
\pic[shift={(0,0,0)}] at (cr4-east) {Box={name=p4,%
        fill=\PoolColor,opacity=0.5,height=15,width=1,depth=15}};
%%%%%%%%%%
% conv5_1,conv5_2,conv5_3
\pic[shift={(1.5,0,0)}] at (p4-east) {RightBandedBox={name=cr5,caption=Convolutional block 5,%
        xlabel={{"256","256","256"}},zlabel=2,fill=\ConvColor,bandfill=\ConvReluColor,%
        height=15,width={7,7,7},depth=15}};
%pool5
\pic[shift={(0,0,0)}] at (cr5-east) {Box={name=p5,%
        fill=\PoolColor,opacity=0.5,height=10,width=1,depth=10}};
%%%%%%%%%%
% fc6
\pic[shift={(3,0,0)}] at (p5-east) {RightBandedBox={name=fc6,caption=FC1,%
        xlabel={{"1",""}},zlabel=256,fill=\FcColor,bandfill=\FcReluColor,%
        height=3,width=3,depth=100}};

\pic[shift={(3.5,0,15)}] at (p5-east) {Ball={name=elt1,%
fill=\SumColor,opacity=0.6,%
radius=2.5,logo=$+$}};

\pic[shift={(3,0,20)}] at (p5-east) {Box={name=fc66,caption=Auxiliary input,%
        xlabel={{"1",""}},zlabel=5,fill=\FcColor,%
        height=3,width=3,depth=10}};

%%%%%%%%%%
% fc7
\pic[shift={(2,0,0)}] at (fc6-east) {RightBandedBox={name=fc7,caption=FC2,%
        xlabel={{"1","dummy"}},zlabel=256,fill=\FcColor,bandfill=\FcReluColor,%
        height=3,width=3,depth=100}};
%%%%%%%%%%
% fc8
\pic[shift={(1.5,0,0)}] at (fc7-east) {RightBandedBox={name=fc8,caption=FC3 + relu,%
        xlabel={{"1","dummy"}},fill=\FcColor,bandfill=\FcReluColor,%
        height=3,width=3,depth=5}};

%%%%%%%%%%
% softmax
\pic[shift={(0,0,0)}] at (fc8-east) {Box={name=softmax,%
        xlabel={{"","dummy"}},zlabel=1,opacity=0.8,fill=\SoftmaxColor,%
        height=3,width=1.5,depth=5}};

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Draw Arrow Connections
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\draw [connection]  (p1-east)        -- node {\midarrow} (cr2-west);
\draw [connection]  (p2-east)        -- node {\midarrow} (cr3-west);
\draw [connection]  (p3-east)        -- node {\midarrow} (cr4-west);
\draw [connection]  (p4-east)        -- node {\midarrow} (cr5-west);
\draw [connection]  (p5-east)        -- node {\midarrow} (fc6-west);
\draw [connection]  (p5-east)        -- node {\midarrow} (fc6-west);
\draw [connection]  (fc6-east)       -- node {\midarrow} (fc7-west);
\draw [connection]  (fc7-east)       -- node {\midarrow} (fc8-west);
\draw [connection]  (fc66-east)      -- node {} (fc6-near);
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Draw Dotted Edges 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\draw[densely dashed]
    (fc6-west)++(0, 1.5*.2, 1.5*.2) coordinate(a) -- (p5-nearnortheast)
    (fc6-west)++(0,-1.5*.2, 1.5*.2) coordinate(b) -- (p5-nearsoutheast)
    (fc6-west)++(0,-1.5*.2,-1.5*.2) coordinate(c) -- (p5-farsoutheast)
    (fc6-west)++(0, 1.5*.2,-1.5*.2) coordinate(d) -- (p5-farnortheast)

>>>>

\def\ConvColor{rgb:yellow,5;red,2.5;white,5}
\def\ConvReluColor{rgb:yellow,5;red,5;white,5}
\def\PoolColor{rgb:red,1;black,0.3}
\def\FcColor{rgb:blue,5;red,2.5;white,5}
\def\FcReluColor{rgb:blue,5;red,5;white,5}
\def\SoftmaxColor{rgb:magenta,5;black,7}
\def\AuxColor{rgb:blue,5;green,15;white,5}
\def\AuxReluColor{rgb:blue,5;green,7.5;white,5}

@@

% conv1_1,conv1_2
\pic[shift={(0,0,0)}] at (0,0,0) {RightBandedBox={name=cr1,caption=Convolutional block 1,%
        xlabel={{"32","32"}},ylabel=32,zlabel=32,fill=\ConvColor,bandfill=\ConvReluColor,%
        height=40,width={2,2},depth=40}};
%pool1
\pic[shift={(0,0,0)}] at (cr1-east) {Box={name=p1,%
        fill=\PoolColor,opacity=0.5,height=35,width=1,depth=35}};
%%%%%%%%%%
% conv2_1,conv2_2
\pic[shift={(2,0,0)}] at (p1-east) {RightBandedBox={name=cr2,caption=Convolutional block 2,%
        xlabel={{"64","64"}},zlabel=16,fill=\ConvColor,bandfill=\ConvReluColor,%
        height=35,width={3,3},depth=35}};
%pool2
\pic[shift={(0,0,0)}] at (cr2-east) {Box={name=p2,%
        fill=\PoolColor,opacity=0.5,height=30,width=1,depth=30}};
%%%%%%%%%%
% conv3_1,conv3_2
\pic[shift={(2,0,0)}] at (p2-east) {RightBandedBox={name=cr3,caption=Convolutional block 3,%
        xlabel={{"128","128","128"}},zlabel=8,fill=\ConvColor,bandfill=\ConvReluColor,%
        height=30,width={4,4,4},depth=30}};
%pool3
\pic[shift={(0,0,0)}] at (cr3-east) {Box={name=p3,%
        fill=\PoolColor,opacity=0.5,height=23,width=1,depth=23}};
%%%%%%%%%%
% conv4_1,conv4_2,conv4_3
\pic[shift={(1.8,0,0)}] at (p3-east) {RightBandedBox={name=cr4,caption=Convolutional block 4,%
        xlabel={{"256","256","256"}},zlabel=4,fill=\ConvColor,bandfill=\ConvReluColor,%
        height=23,width={7,7,7},depth=23}};
%pool4
\pic[shift={(0,0,0)}] at (cr4-east) {Box={name=p4,%
        fill=\PoolColor,opacity=0.5,height=15,width=1,depth=15}};
%%%%%%%%%%
% conv5_1,conv5_2,conv5_3
\pic[shift={(1.5,0,0)}] at (p4-east) {RightBandedBox={name=cr5,caption=Convolutional block 5,%
        xlabel={{"256","256","256"}},zlabel=2,fill=\ConvColor,bandfill=\ConvReluColor,%
        height=15,width={7,7,7},depth=15}};
%pool5
\pic[shift={(0,0,0)}] at (cr5-east) {Box={name=p5,%
        fill=\PoolColor,opacity=0.5,height=10,width=1,depth=10}};
%%%%%%%%%%
% fc6
\pic[shift={(3,0,0)}] at (p5-east) {Box={name=fc6,caption=Concatenation layer,%
        xlabel={{"1",""}},zlabel=256,fill=\FcColor,%
        height=3,width=3,depth=100}};

\pic[shift={(3,0,-11)}] at (p5-east) {Box={name=fc66,caption=Auxiliary input,%
        xlabel={{"",""}},zlabel=5,fill=\AuxColor,%
        height=3,width=3,depth=10}};

%%%%%%%%%%
% fc7
\pic[shift={(2,0,0)}] at (fc6-east) {RightBandedBox={name=fc7,caption=Dense layer,%
        xlabel={{"1","dummy"}},zlabel=256,fill=\FcColor,bandfill=\FcReluColor,%
        height=3,width=3,depth=100}};
%%%%%%%%%%
% fc8
\pic[shift={(1.5,0,0)}] at (fc7-east) {RightBandedBox={name=fc8,caption=Output layer,%
        xlabel={{"1","dummy"}},fill=\FcColor,bandfill=\FcReluColor,%
        height=3,width=3,depth=5}};

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Draw Arrow Connections
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\draw [connection]  (p1-east)        -- node {\midarrow} (cr2-west);
\draw [connection]  (p2-east)        -- node {\midarrow} (cr3-west);
\draw [connection]  (p3-east)        -- node {\midarrow} (cr4-west);
\draw [connection]  (p4-east)        -- node {\midarrow} (cr5-west);
\draw [connection]  (p5-east)        -- node {\midarrow} (fc6-west);
\draw [connection]  (p5-east)        -- node {\midarrow} (fc6-west);
\draw [connection]  (fc6-east)       -- node {\midarrow} (fc7-west);
\draw [connection]  (fc7-east)       -- node {\midarrow} (fc8-west);

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Draw Dotted Edges 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\draw[densely dashed]
    (fc6-west)++(0, 1.5*.2, 1.5*.2) coordinate(a) -- (p5-nearnortheast)
    (fc6-west)++(0,-1.5*.2, 1.5*.2) coordinate(b) -- (p5-nearsoutheast)
    (fc6-west)++(0,-1.5*.2,-1.5*.2) coordinate(c) -- (p5-farsoutheast)
    (fc6-west)++(0, 1.5*.2,-1.5*.2) coordinate(d) -- (p5-farnortheast)
